Network Configuration Synthesis with Abstract Topologies

### 2016-11-09 paper/abstraction/paper.tex
add concretization theorem
stashing changes

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}

@@

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)

@@

  \caption{ABGP syntax (a), compilation from product graphs (b), Policy concretization (c), and ABGP concretization (d).}
  \label{fig:abgp-syntax}

@@

>>>>

\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}

@@

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& d.d.d.d/[d..d] ~~~~~~~~~~~~~~~~~~~  & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)

@@

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}

@@

\begin{thm}
  For any context $\Gamma$, concrete topology $G$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
  $$\Con(\text{compile}(pol), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f))$$
\end{thm}
